Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-09-17 main.tex
updates in Section 4

Whenever $T$ is any $n$-dimensional simplex $T$,
we define the \textit{geometric shape measure} $\kappa(T)$,
the \textit{aspect shape measure} $\kappa_{\maxcol}(T)$,
and 
the \textit{algebraic shape measure} $\kappa_{2}(T)$
by 
\begin{align}\label{math:shapemeasure}
    \kappa(T)
    := 
    \frac{ \diam(T)^{n} }{ n! \vol(T) }
    ,
    \qquad 
    \kappa_{\maxcol}(T)
    := 
    \frac{ \diam(T) }{ \height(T) }
    ,
    \qquad 
    \kappa_{2}(T)
    := 
    \sup_{ \varphi : \Delta^n \rightarrow T } 
    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
%     \sup_{ \varphi : \Delta^n \rightarrow T } \| \Jacobian \varphi \|_{\maxcol} \| \Jacobian \varphi^{-1} \|_{\maxcol}
    ,
\end{align}
where the last supremum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
% DONE: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.

When $\calT$ is an $n$-dimensional simplicial complex, we naturally introduce 
\begin{align}\label{math:shapemeasure:triangulation}
    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T)
    ,
    \quad 
    \kappa_{\maxcol}(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa_{\maxcol}(T)
    ,
    \quad 
    \kappa_{2}(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa_{2}(T)
    .
\end{align}
We call these the geometric, aspect, and algebraic shape measure, respectively, of the triangulation.

@@

\begin{lemma}\label{lemma:measurerelationships}
    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
    \begin{gather*}
        \| \Jacobian \varphi \|
        \leq 
        \Ceins{n} \cdot \diam(T) % DONE: can this improved?
        ,
        \qquad 
        \| \Jacobian \varphi^{-1} \|
        \leq 
        \Czwei{n} \cdot 
        \kappa(T) 
        \diam(T)^{-1}
        ,
        \\
        \kappa_{2}(T)
        \leq 
        \Cdrei{n}
        % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
        \kappa(T)
        ,
        \qquad 
        %         \kappa(T)^{\frac 1 n}
        %         \leq 
        \kappa_{\maxcol}(T)
        \leq 
        \kappa(T)
        .
    \end{gather*}
    Here,
    \begin{align*}
        \Ceins{n} \leq \sqrt{n},
        \quad 
        \Czwei{n} \leq          \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}, 
        \quad 
        \Cdrei{n} \leq \Ceins{n}\Czwei{n} %\sqrt{n} \left( \frac{n}{n-1} \right)^{\frac{n-1}{2}}
        . 
    \end{align*}
\end{lemma}
\begin{proof}
%     The columns of the matrix $\Jacobian \varphi^{-1}$ are the gradients of the barycentric coordinates of the vertices of $T$,
%     except for the vertex $\varphi(0)$. It immediately follows that 
%     \begin{align*}
%         \| \Jacobian \varphi^{-1} \|_{2} \leq \sqrt{n} \cdot \height(T)^{-1}
%         .
%     \end{align*}
%     The smallest height in the reference simplex $\Delta^{n}$ is $1/\sqrt{n}$. 
%     
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
    The Jacobian determinant is the product of these singular values. 
    By a result of Hong and Pan \cite{hong1992lower},
    \begin{align*}
        \sigma_{n}
        &\geq 
        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n-1} }
        = 
        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
        \frac{ n! \vol(T) }{ \diam(T)^{n-1} }
        .
    \end{align*}
%     To get the second inequality, we multiple the last term by $\sigma_{1} / ( \sqrt{n} \diam(T) ) \leq 1$.
    The second inequality follows by taking the reciprocal. 
    The definition of the condition number now gives the third inequalities. 
    % To get the third inequality, we divide both sides by $\sigma_{1}$ and use $\sigma_{1} \leq \sqrt{n} \diam(T)$.
    Finally, 
    if $F$ is the face of $T$ opposite to the vertex with the smallest height, then 
    \begin{align*}
        \frac{ \diam(T) }{ \height(T) }
        \leq 
        \frac{ \diam(T) \vol(F) }{ n \vol(T) }
        \leq 
        \frac{ \diam(T)^{n} }{ n! \vol(T) }
        .
    \end{align*}
%     Since $n! \vol(T)$ is bounded from below by the product of any $n$ different heights of $T$, it follows that 
%     \begin{align*}
%         \frac{ \diam(T)^{n} }{ n! \vol(T) }
%         \leq 
%         \frac{ \diam(T)^{n} }{ \height(T)^{n} }
%         .
%     \end{align*}
    That shows the fourth and last of the inequalities. 
\end{proof}

\begin{remark}
    Whenever $T$ is an $n$-dimensional simplex, the ratio $\kappa(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    In our convention, the reference simplex has unit shape measure.
    For example, $\kappa(T)=1$ whenever $T$ is a line segment, an isosceles right-angled triangle, or the generalizations of these reference simplices to higher dimensions. $\kappa(T)$ is slightly bigger than one for equilateral simplices and blows up with distortion.

% Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
    The geometric ratio $\kappa(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}. 
    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
% TODO     (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
\end{remark}

We are interested in the maximal ratio of volumes between neighboring $n$-simplices: 
\begin{align}\label{math:volumecomparisonmeasure}
    \rho(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
\end{align}
We also want to compare the diameters of simplices that intersect. We define 
\begin{align}\label{math:diametercomparison}
    \theta(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
    \frac{ \diam(T) }{ \diam(T') }
\end{align}
Whenever $S,T$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
that preserves $F$. We define 
\begin{align}\label{math:reflectionmeasure}
    \xi(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
    \| \Jacobian \Xi_{S,T} \|
\end{align}
to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
This indicator quantifies how much reflection across the shared face distorts the geometry.

% and $\varphi : \Delta^{n} \rightarrow T$ is an affine diffeomorphism from the reference simplex,
% we define the quantity 
% \begin{align*}
%     \kappa(T)
%     := 
%     \frac{ \diam(T)^{n} }{ n! \vol(T) }
%     .
% \end{align*}

\begin{lemma}\label{lemma:volumecomparison}
    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
    \begin{align*}
        \diam(T_1)
        \leq 
        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        % \diam(F)
        % = 
        \kappa(T_1)
        \diam(F)
        ,
        \qquad 
        \frac{ \vol(T_1) }{ \vol(T_2) }
        \leq 
        % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
        % \cdot 
        % \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
        % = 
        \kappa(T_1) \kappa(T_2)
        .
    \end{align*}
    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
    \begin{align*}
        \| \Jacobian \Xi \|
        \leq 
        \Cvier{n}
        \kappa(T_2)^{-1} \kappa(T_1) 
        % \frac{ \kappa(T_1) }{ \kappa(T_2) }
        .
    \end{align*}
    Here, $\Cvier{n} \leq \Ceins{n} \Czwei{n}$. 
\end{lemma}

@@

\begin{proof}
    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
    By the volume formula for simplices, $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
    The diameter of $F$ is at least as large as the height $h_S$ of some other facet $S$ of $T$. Recursive application of the volume formula shows 
    \begin{align*}
        \vol(T) = \frac{1}{n!} h_S h_2 \cdots h_n,
    \end{align*}
    where $h_S \leq \diam(F)$ and $h_2, \cdots, h_n \leq \diam(T)$. Now, 
    \begin{align*}
        \diam(T) \frac{ n! \vol(T) }{ \diam(T)^{n} } \leq h_S \leq \diam(F).
    \end{align*}
    The first estimate follows. 
    On the other hand, 
    \begin{align*}
        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n \cdot \vol(T_1)} \diam(F),
        \\
        h_2 &= n \frac{\vol(T_2)}{\vol(F)} \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
        .
    \end{align*}
    The second estimate follows. 
    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, Lemma~\ref{lemma:measurerelationships} and the first estimate imply 
    \begin{align*}
        \| \Jacobian \Xi \|
        &
        \leq 
        \Ceins{n}
        \Czwei{n}
        \kappa(T_2)
        \diam(T_1)
        \diam(T_2)^{-1}
        \\&
        \leq 
        \Ceins{n}
        \Czwei{n}
        \kappa(T_2)
        \kappa(T_1) 
        \diam(F)
        \diam(T_2)^{-1}
        \leq 
        \Ceins{n}
        \Czwei{n}
        \kappa(T_2)
        \kappa(T_1) 
        .
    \end{align*}
    All the desired results thus follow.

%     \todo{Tighter estimate via geometry}
%     Without loss of generality, $F$ lies in the plane of the second to last coordinates,
%     so that the height of $T_1$ and $T_2$ is in the first coordinate direction. 
%     After further rotation, we can assume that $z_2 = a_1 e_1 + a_2 e_2$ for some $a_1, a_2 \in \bbR$.
%     If $h > 0$ is the height of $z_1$ within $T_1$, then the singular values of $\Xi$ 
%     are all one with the possibe exception of the singular values of the matrix 
%     \begin{align*}
%         A = 
%         \begin{pmatrix}
%             a_1/h & 0
%             \\
%             a_2/h & 1
%         \end{pmatrix}
%     \end{align*}
%     Its singular values are 
%     \begin{align*}
%         \sigma_{\max}
%         &= 
%         \frac{1}{\sqrt 2}
%         \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
%         \\&= 
%         \frac{1}{\sqrt 2}
%         \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\sqrt{ 
%             \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
%             \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
%             } }
%         \\&= 
%         \frac{1}{\sqrt 2}
%         \sqrt{ 
%             \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h} \right)
%             }
%         +
%         \frac{1}{\sqrt 2}
%         \sqrt{ 
%             \frac 1 2 \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h} \right)
%             }
%         \\&= 
%         \frac{1}{2}
%         \sqrt{ 
%             1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
%             }
%         +
%         \frac{1}{2}
%         \sqrt{ 
%             1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
%             }
%         \\&= 
%         \frac{1}{2}
%         \sqrt{ 
%             \left( 1 + \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
%             }
%         +
%         \frac{1}{2}
%         \sqrt{ 
%             \left( 1 - \frac{ a_1 }{h} \right)^{2} + \frac{ a_2^2 }{h^2}
%             }
%         ,
%         \\
%         \sigma_{\min}
%         &=
%         \frac{1}{\sqrt 2}
%         \sqrt{ 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} - \sqrt{ \left( 1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} \right)^2 - 4 \frac{ a_1^2 }{h^2} } }
%         \\&= 
%         \frac{1}{2}
%         \sqrt{ 
%             1 + \frac{ a_1^2 }{h^2} + \frac{ a_2^2 }{h^2} + 2\frac{ a_1 }{h}
%             }
%         -
%         \frac{1}{2}
%         \sqrt{ 
%             1 + \frac{ a_1^2 }{h^2} - \frac{ a_2^2 }{h^2} - 2\frac{ a_1 }{h}
%             }
%         .
%     \end{align*}
\end{proof}

\begin{remark}
    Lemma~\ref{lemma:volumecomparison} fully controls the shape quantity $\rho(\calT)$ but not $\theta(\calT)$. 
    As seen above, we can bound the ratio of diameters and volumes of simplices that share at least one edge in terms of the shape measure. 
    If we have an upper estimate for the number of simplices sharing a given vertex, 
    we can also bound the ratios of diameters and volumes of simplices sharing only a single common vertex. 
\end{remark}
%%%%%%%% END HERE

>>>>

Whenever $T$ is any $n$-dimensional simplex $T$,
we define the \textit{geometric shape measure} $\geometricshapemeasure(T)$,
the \textit{aspect shape measure} $\aspectratio(T)$,
and 
the \textit{algebraic shape measure} $\algebraicshapemeasure(T)$
by 
\begin{align}\label{math:shapemeasure}
    \geometricshapemeasure(T)
    := 
    \frac{ \diam(T)^{n} }{ n! \vol(T) }
    ,
    \qquad 
    \aspectratio(T)
    := 
    \frac{ \diam(T) }{ \height(T) }
    ,
    \qquad 
    \algebraicshapemeasure(T)
    := 
    \sup_{ \varphi : \Delta^n \rightarrow T } 
    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
%     \sup_{ \varphi : \Delta^n \rightarrow T } \| \Jacobian \varphi \|_{\maxcol} \| \Jacobian \varphi^{-1} \|_{\maxcol}
    ,
\end{align}
where the last supremum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
% DONE: Although this is fairly clear upon reading, we could specify in word that $\geometricshapemeasure(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\volumeratio(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.

When $\calT$ is an $n$-dimensional simplicial complex, we naturally introduce 
\begin{align}\label{math:shapemeasure:triangulation}
    \geometricshapemeasure(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \geometricshapemeasure(T)
    ,
    \quad 
    \aspectratio(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \aspectratio(T)
    ,
    \quad 
    \algebraicshapemeasure(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \algebraicshapemeasure(T)
    .
\end{align}
We call these the geometric, aspect, and algebraic shape measure, respectively, of the triangulation.

@@

\begin{lemma}\label{lemma:measurerelationships}
    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
    \begin{gather*}
        \| \Jacobian \varphi \|
        \leq 
        \Ceins{n} \cdot \diam(T) % DONE: can this improved?
        ,
        \qquad 
        \| \Jacobian \varphi^{-1} \|
        \leq 
        \Czwei{n} \cdot 
        \geometricshapemeasure(T) 
        \diam(T)^{-1}
        ,
        \\
        \algebraicshapemeasure(T)
        \leq 
        \Cdrei{n}
        % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
        \geometricshapemeasure(T)
        ,
        \qquad 
        %         \geometricshapemeasure(T)^{\frac 1 n}
        %         \leq 
        \aspectratio(T)
        \leq 
        \geometricshapemeasure(T)
        .
    \end{gather*}
    Here,
    \begin{align*}
        \Ceins{n} \leq \sqrt{n},
        \quad 
        \Czwei{n} \leq          \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}, 
        \quad 
        \Cdrei{n} \leq \Ceins{n}\Czwei{n} %\sqrt{n} \left( \frac{n}{n-1} \right)^{\frac{n-1}{2}}
        . 
    \end{align*}
\end{lemma}
\begin{proof}
%     The columns of the matrix $\Jacobian \varphi^{-1}$ are the gradients of the barycentric coordinates of the vertices of $T$,
%     except for the vertex $\varphi(0)$. It immediately follows that 
%     \begin{align*}
%         \| \Jacobian \varphi^{-1} \|_{2} \leq \sqrt{n} \cdot \height(T)^{-1}
%         .
%     \end{align*}
%     The smallest height in the reference simplex $\Delta^{n}$ is $1/\sqrt{n}$. 
%     
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
    The Jacobian determinant is the product of these singular values. 
    By a result of Hong and Pan \cite{hong1992lower},
    \begin{align*}
        \sigma_{n}
        &\geq 
        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n-1} }
        = 
        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
        \frac{ n! \vol(T) }{ \diam(T)^{n-1} }
        .
    \end{align*}
%     To get the second inequality, we multiple the last term by $\sigma_{1} / ( \sqrt{n} \diam(T) ) \leq 1$.
    The second inequality follows by taking the reciprocal. 
    The definition of the condition number now gives the third inequalities. 
    % To get the third inequality, we divide both sides by $\sigma_{1}$ and use $\sigma_{1} \leq \sqrt{n} \diam(T)$.
    Finally, 
    if $F$ is the face of $T$ opposite to the vertex with the smallest height, then 
    \begin{align*}
        \frac{ \diam(T) }{ \height(T) }
        \leq 
        \frac{ \diam(T) \vol(F) }{ n \vol(T) }
        \leq 
        \frac{ \diam(T)^{n} }{ n! \vol(T) }
        .
    \end{align*}
%     Since $n! \vol(T)$ is bounded from below by the product of any $n$ different heights of $T$, it follows that 
%     \begin{align*}
%         \frac{ \diam(T)^{n} }{ n! \vol(T) }
%         \leq 
%         \frac{ \diam(T)^{n} }{ \height(T)^{n} }
%         .
%     \end{align*}
    That shows the fourth and last of the inequalities. 
\end{proof}

\begin{remark}
    Whenever $T$ is an $n$-dimensional simplex, the ratio $\geometricshapemeasure(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    In our convention, the reference simplex has unit shape measure.
    For example, $\geometricshapemeasure(T)=1$ whenever $T$ is a line segment, an isosceles right-angled triangle, or the generalizations of these reference simplices to higher dimensions. $\geometricshapemeasure(T)$ is slightly bigger than one for equilateral simplices and blows up with distortion.

% Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
    The geometric ratio $\geometricshapemeasure(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}. 
    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
% TODO     (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
\end{remark}

We are interested in the maximal ratio of volumes between neighboring $n$-simplices, written $\volumeratio(\calT)$,
and the ratio of intersecting simplices, written $\diameterratio(\calT)$. Formally, 
\begin{align}
    \volumeratio(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } 
    \frac{ \vol(T) }{ \vol(T') }
    ,
    \qquad 
    \diameterratio(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
    \frac{ \diam(T) }{ \diam(T') }
    .
\end{align}
Whenever $T, T'$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{T,T'} : T \rightarrow T'$ denote the affine diffeomorphism 
that preserves $F$. We define 
\begin{align}\label{math:reflectionmeasure}
    \reflectionestimate(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
    \| \Jacobian \Xi_{T,T'} \|
\end{align}
to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
This indicator quantifies how much reflection across the shared face distorts the geometry.

% and $\varphi : \Delta^{n} \rightarrow T$ is an affine diffeomorphism from the reference simplex,
% we define the quantity 
% \begin{align*}
%     \geometricshapemeasure(T)
%     := 
%     \frac{ \diam(T)^{n} }{ n! \vol(T) }
%     .
% \end{align*}

\begin{lemma}\label{lemma:volumecomparison}
    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
    \begin{align*}
        \diam(T_1)
        \leq 
        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        % \diam(F)
        % = 
        \geometricshapemeasure(T_1)
        \diam(F)
        ,
        \qquad 
        \frac{ \vol(T_1) }{ \vol(T_2) }
        \leq 
        % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
        % \cdot 
        % \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
        % = 
        \aspectratio(T_1) \aspectratio(T_2)
        .
    \end{align*}
    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism that is the identity over $F$, then 
    \begin{align*}
        \| \Jacobian \Xi \|
        \leq 
        ( 1 + \aspectratio(T_2) ) \aspectratio(T_1)
        % \Cvier{n} \geometricshapemeasure(T_2) \geometricshapemeasure(T_1) 
        .
    \end{align*}
%     Here, $\Cvier{n} \leq \Ceins{n} \Czwei{n}$. 
\end{lemma}

@@

\begin{proof}
    The diameter of $F$ is at least as large as the height $h_S$ of some other facet $S$ of $T_{1}$. 
%     Recursive application of the volume formula shows $n! \cdot \vol(T) = h_S h_2 \cdots h_n$,
%         n! \cdot \vol(T) = \frac{1}{n!} h_S h_2 \cdots h_n,
%     where $h_S \leq \diam(F)$ and $h_2, \cdots, h_n \leq \diam(T_{1})$. 
    Now, 
%        \diam(T) \frac{ n! \vol(T) }{ \diam(T)^{n} } \leq h_S \leq \diam(F).
        \diam(T_{1}) \aspectratio(T_{1})^{-1} \leq \height(T_{1}) \leq h_S \leq \diam(F).
    The first estimate follows. 
    As for the second estimate,
    let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
    By the volume formula for simplices, $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$. Thus follows the second estimate: 
        \frac{ \vol(T_1) }{ \vol(T_2) }
        \frac{ h_1 }{ h_2 }
        \frac{ \diam(T_1) }{ h_2 }
        \aspectratio(T_{1}) \frac{ \diam(F) }{ h_2 }
        \aspectratio(T_{1}) \aspectratio(T_{2})
    On the other hand, 
        % h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n \cdot \vol(T_1)} \diam(F),
%         \\
%         h_2 &= n \frac{\vol(T_2)}{\vol(F)} \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
        h_1 \leq \aspectratio(T_{1}) \diam(F),
        \qquad 
        h_2 \geq \aspectratio(T_{2})^{-1} \diam(T_2)\geq \aspectratio(T_{2})^{-1} \diam(F)
    The second estimate follows. 
    Lastly, $\Xi : T_1 \rightarrow T_2$ be as above
    can be written as the composition $\Xi = \phi_{2} \phi^{-1}_{1}$ for some affine transformations $\phi_1 : \Delta^{n} \rightarrow T_1$ and $\phi_2 : \Delta^{n} \rightarrow T_2$. 
    Lemma~\ref{lemma:measurerelationships} and the first estimate imply 
        \| \Jacobian\phi_{2} \| \cdot \| \Jacobian\phi_{1}^{-1} \|
        \Ceins{n}^{2} \diam(T_2) \height(T_1)^{-1}
        \Ceins{n}^{2} \aspectratio(T_2) \diam(F) \height(T_1)^{-1}
        \Ceins{n}^{2} \aspectratio(T_2) \aspectratio(T_1)
%         \| \Jacobian \Xi \|
%         \Ceins{n}
%         \Czwei{n}
%         \geometricshapemeasure(T_2)
%         \diam(T_1)
%         \diam(T_2)^{-1}
%         \Ceins{n}
%         \Czwei{n}
%         \geometricshapemeasure(T_2)
%         \geometricshapemeasure(T_1) 
%         \diam(F)
%         \diam(T_2)^{-1}
%         \Ceins{n}
%         \Czwei{n}
%         \geometricshapemeasure(T_2)
%         \geometricshapemeasure(T_1) 
    All the desired results thus follow.
\end{comment}
    Lastly, let $\Xi : T_1 \rightarrow T_2$ be as stated. 
    Writing $h_0$ for the unit normal in direction $z_1$, we have 
        \Xi(x) 
        - \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_1
        + \frac{ \langle h_0, x \rangle }{ \langle h_0, z_1 \rangle } z_2
        \qquad 
        x \in \bbR^{n}
    Its Jacobian is the rank-one perturbation of the linear projection along $z_1$ onto the hyperplane spanned by $F$. 
    By the Xu-Zikanatov estimate,
        \frac{ \diam(T_1) }{ \height(T_1) }
        \frac{ \diam(T_2) }{ \height(T_1) }
        \left( 1 + \aspectratio(T_2) \right)
        \aspectratio(T_1)
    The desired estimates are shown.
    \todo{Tighter estimate via geometry}
    Matrix inverse lemma:
        A ( A + (z_2-z_1) e_1^t )^{-1}
        \Id
        \left( 1 + e_1^{t} A^{-1} (z_2-z_1) \right)^{-1}
        (z_2-z_1) e_1^t \cdot A^{-1}
        \Id
        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
        (z_2-z_1) e_1^t \cdot A^{-1}
    Putting in a multiple of $\alpha z_1$, we find 
        \alpha z_1
        \left( e_1^{t} A^{-1} z_2 \right)^{-1}
        (z_2-z_1) 

    Without loss of generality, $F$ lies in the hyerplane plane of the second to last coordinates,
    so that the height of $T_1$ and $T_2$ is in the first coordinate direction. 
    After further rotation, we can assume that $z_1$ and $z_2$ are in the span of the first three coordinate directions with 
    We can write 
    \begin{align*}
        z_1 = a_1 e_1 + a_2 e_2, \qquad z_2 = b_1 e_1 + b_2 e_2 + e_3 b_3.
    \end{align*}
    The face $F$ spans a hyperplane over which $\Xi$ is the identity, and it remains to study the matrix
    \begin{align*}
        A = 
        \begin{pmatrix}
            b_1/a_1 & 0 & 0
            \\
            (b_2-a_2)/a_1 & 1 & 0
            \\
            b_3/a_1 & 0 & 1
        \end{pmatrix}
        =:
        \begin{pmatrix}
            c_1 & 0 & 0
            \\
            c_2 & 1 & 0
            \\
            c_3 & 0 & 1
        \end{pmatrix}
    \end{align*}
    Its singular values are $1$ and 
    \begin{align*}
        \sigma_{\max}
        =
        \frac{1}{\sqrt 2}
        \sqrt{
            1 + c_1^2 + c_2^2 + c_3^2 
            +
            \sqrt{ ( 1 + c_1^2 + c_2^2 + c_3^2 )^2 - 4 c_1^2 }
        }
        =
        \frac{1}{\sqrt 2}
        \sqrt{
            1 + c_1^2 + c_2^2 + c_3^2 
            +
            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
            \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
        }
        =
        \frac{1}{2}
        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
        +
        \frac{1}{2}
        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
        =
        \frac{1}{2}
        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
        +
        \frac{1}{2}
        \sqrt{ ( 1 - c_1 )^2 + c_2^2 + c_3^2 }
        \leq 
        \sqrt{ ( 1 + c_1 )^2 + c_2^2 + c_3^2 }
        .
    \end{align*}
    \begin{align*}
        \sigma_{\max}
        =
        \frac{1}{\sqrt 2}
        \sqrt{
            1 + c_1^2 + c_2^2 + c_3^2 
            -
            \sqrt{ c_1^2 + c_2^2 + c_3^2 - 4 c_1^2 }
        }
        =
        \frac{1}{2}
        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 + 2 c_1 }
        -
        \frac{1}{2}
        \sqrt{ 1 + c_1^2 + c_2^2 + c_3^2 - 2 c_1 }
        .
    \end{align*}
